---
title: "README"
author: "Charles McCann, Dominique Edwards, Hari Narayan Sanadhya, Huynh vu"
date: "April 22, 2017"
output: 
  md_document:
    variant: markdown_github
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Two different studies
 1. Analysis of trunk circumferences with age of the Orange Trees
 2. Comparitive average monthly temperature analysis of various countries, cities throughout the world and also for US land temperatures.
      
## Project Purpose
1. Using the built-in data set called Orange in R, analyze the trunk circumferences of Orange trees based on their age thereby determining growth of the tree. 
2. Given the monthly average temperatures of various countries and cities around the world, analyze the maximum variations in monthly temperatures for countries and cities around the world and also for US land.

## Project Folder and File structure
* Folders: - 
  1. source: - This folder contains the R source code used for tidying the raw datasets.
  2. graphs: - This folder contains all the graphs that are generated during this study.
  3. data: - This folder contains raw data files, the tidied files and merged file.
* Files: -
  1. data/CityTemp.csv: - This is the raw city temperature file containing the monthly average temperatues of various cities around the world.
  2. data/TEMP.csv: - This is the raw temperature file containing the monthly average temperatures of various countries in the World.
  3.data/cleaned_City_Temp_Data.txt: - Tab delimited tidied version of city temperature file (CityTemp.csv) generated by the execution of the R code 'tidy_city_temp.R'.
  4. data/cleaned_GDP_Data.txt: - Tab delimited tidied version of temperature file (Temp.csv) generated by the execution of the R code 'tidy_temp.R'.
  5. data/difference_of_average_US_land_temperature_by_year.txt: - Tab delimited file containing the one year difference of average US land temperature by year since 01/01/1990.
  6. data/max_variation_in_monthly_avg_temp_by_country.txt: - Tab delimited file containing the maximum monthly average temperature variation by country since 01/01/1990.
  7. graphs/Average US land temperature by year.png: - This is the plot of the average US land temperature by year since 01/01/1900.
  8. graphs/Maximum Temp Variation.png: - This is the plot of top 20 countries with maximum average temperature variations since 01/01/1900.
  9. graphs/Maximum Temp Variation-City.png: - This is the plot of top 20 cities with maximum average temperature variations since 01/01/1900.
  10. graphs/Scatter plot of circumference vs age.png: - This is a scatter plot of the trunk circumferences against the age of the Orange tree.
  11. graphs/Boxplot of circumference by tree.png: - This is a box plot of the trunk circumferences by Orange tree.
  12. source/orange.R: - R code that performs the required analysis of the built-in Orange data set.
  13. source/Temp-Analysis.R: - R code that performs all the required analysis on the Temp and CityTemp data.
  14. source/tidy_city_temp.R: - R code that performs the tidying of the raw city temperature data file (CityTemp.csv).
  15. source/tidy_temp.R: - R code that performs the tidying of the raw temperature data file (Temp.csv).
  16. source/install_package.R: - R code that installs all the required R packages used in this project (namely doBy, ggplot2, dplyr and lubridate).
  17. README.md: - This markdown file includes an explanation of the purpose of the project and the other files.
  18. README.Rmd: - The R markdown file that creates the README.md file.
  19. report_orange.md: - This markdown file provides the details of the analysis performed on the built-in data set Orange including the introduction, analysis code, output of the code and conclusion derived from the analysis.
  20. report_orange.Rmd: - The R markdown file that creates the report_orange.md file.
  21. report_temp.md: - This markdown file provides the details of the analysis performed on the tidied temperature data including the introduction, analysis code, output of the code and conclusion derived from the analysis.
  22. report_temp.Rmd: - The R markdown file that creates the report_temp.md file.
  23. Makefile: - It lists all the steps to regenerate this study.
  24. CaseStudy2.Rproj: - This is the R project file for this project.
  25. .gitignore: - This file specifies intentionally untracked files that Git should ignore. 

  
# Session Information
```{r echo=FALSE}
sessionInfo()
```
